Seniors remain the most vulnerable population group as Toronto enters the 6th wave of COVID-19

### 2022-04-24 outputs/paper/paper.Rmd
hide code
add keyboard

---
title: "Seniors remain the most vulnerable population group as Toronto enters the 6th wave of COVID-19"
subtitle: "An analysis of the COVID-19 pandemic in Toronto with an emphasis on the past six months"
author: Ka Chun Mo
thanks: "Code and data are available at: https://github.com/francomomo/covid_19_toronto."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Ontario is relaxing its COVID-19 measures even though health care experts are predicting an incoming sixth wave of COVID-19. It is crucial for us to continue taking measures to protect ourselves and the people around us and to seek insights to keep ourselves inform. In this paper, we provide an up-to-date analysis of the various aspects of COVID-19 with an emphasis of the past six months. We found that seniors are still the most susceptible population group after two years into the COVID-19 pandemic."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

```{r model-result, echo='FALSE'}
model_data <- covid_data %>%
  mutate(fat=
           case_when(outcome=='FATAL' ~ 1,
                     outcome=='RESOLVED' ~ 0))

>>>>

---
title: "Seniors remain the most vulnerable population group as Toronto enters the 6th wave of COVID-19"
subtitle: "An analysis of the COVID-19 pandemic in Toronto with an emphasis on the past six months"
author: Ka Chun Mo
thanks: "Code and data are available at: https://github.com/francomomo/covid_19_toronto."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Ontario is relaxing its COVID-19 measures even though health care experts are predicting an incoming sixth wave of COVID-19. It is crucial for us to continue taking measures to protect ourselves and the people around us and to seek insights to keep ourselves inform. In this paper, we provide an up-to-date analysis of the various aspects of COVID-19 with an emphasis of the past six months. We found that seniors are still the most susceptible population group after two years into the COVID-19 pandemic. \\par \\textbf {Keywords:} COVID-19, COVID-19 in Toronto, Toronto, Canada"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

```{r model-result, echo=FALSE}
model_data <- covid_data %>%
  mutate(fat=
           case_when(outcome=='FATAL' ~ 1,
                     outcome=='RESOLVED' ~ 0))
